Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-08-02 paper/revision/responseToreviewers.tex

I only have some minor indications that I think they can improve a little bit this paper.

\begin{enumerate}
\item The use of the letter beta should be clarified because its use in expressions (5, 8a, 8b and 8c) and in lines 104-105, seems not to be the same that its use in expressions (4a, 4b y 4c) or, for example, in tables 3 and 4.\\
$\rightarrow$ Done, The $\beta$ value is the same, the choice of the $\beta$-divergence in the equation 4 influes the way the expressions 5 and 8 are then updated. This has been precised . 'Thus, the choice of the $\beta$-divergence in the equation affects how the matrix $\mathbf{H}$ is updated.' (section 2.1).

\item In relation with table 4, it may be appropriate that it includes some more complete representation or table of results, for the reader interested in analyzing in more detail the effects that the different variables analyzed may have on errors. For example, one in which, varying one of the variables analyzed, the others remain constant.

$\rightarrow$ We added a part dedicated to this where the evolution of the cost functions and the $MAE$ errors are displayed according to the iteration (section 5).

### 2018-08-02 paper/revision/articleNmfTrafficSimScene2018_v2.tex
review done, ready to proofread

@@

Finally, TI-NMF presents the most performing results, except in the \textit{park} environment ($MAE$ = 2.95 dB). In this sound environment, with the threshold value $t_h$ = 0.32, the traffic dictionary is composed, on average, of 136 elements.
By increasing this value, it would be possible to put aside the spectra furthest away of the traffic elements and then decrease the error. For the rest of the sound environments, TI-NMF has the lowest errors. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). With on average 198 elements in $\mathbf{W}_{traffic}$, almost all the elements present in $\mathbf{W'}$ can be considered as traffic elements.

Considering a unique dictionary fitted to the sound scene under evaluation thus makes TI-NMF very effective when traffic is predominant, while the thresholding step make it possible to discards the elements of the dictionary that deviate too much when the traffic is less present.

>>>>

\begin{figure*}[t]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionCost_AA.pdf}
\caption{Evolution of the cost function.} \label{fig:grafic_cost}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionMAE_AA.pdf}
\caption{Evolution of the $MAE$ errors.} \label{fig:grafic_mae}
\end{subfigure}
\caption{Normalized reconstruction error of the global sound mixtures \subref{fig:grafic_cost} and the traffic component \subref{fig:grafic_mae} for each sound environment.} \label{fig:grafic_cost_mae}
\end{figure*}

@@

Finally, TI-NMF presents the most performing results, except in the \textit{park} environment ($MAE$ = 2.95 dB). In this sound environment, with the threshold value $t_h$ = 0.32, the traffic dictionary is composed, on average, of 136 elements.
By increasing this value, it would be possible to put aside the spectra furthest away of the traffic elements and then decrease the error. For the rest of the sound environments, TI-NMF has the lowest errors. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). With on average 198 elements in $\mathbf{W}_{traffic}$, almost all the elements present in $\mathbf{W'}$ can be considered as traffic elements. 
Considering a unique dictionary fitted to the sound scene under evaluation thus makes TI-NMF very effective when traffic is predominant, while the thresholding step make it possible to discards the elements of the dictionary that deviate too much when the traffic is less present.

\begin{figure*}[t!]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionK_AA.pdf}
\caption{Influence of the experimental factor $K$ (TI-NMF, $w_t$ = 0.5 s, $\beta$ = 2, $t_h$ = 0.32.} \label{fig:grafic_K}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionWt_AA.pdf}
\caption{Influence of the experimental factor $K$ (TI-NMF, $K$ = 200 s, $\beta$ = 2, $t_h$ = 0.32.} \label{fig:grafic_wt}
\end{subfigure}
\caption{Influence of the number of elements $K$ \subref{fig:grafic_K} and the temporal frame $w_t$ \subref{fig:grafic_wt} on the $mMAE$ error with the best TI-NMF obtained in Table \ref{tab:results}.} \label{fig:grafic_K_wt}
\end{figure*}

To visualized the behavior of this approach, the evolution of the normalized cost function ($D(\mathbf{V}\Vert \mathbf{WH})/(F\times N)$ as the duration of each audio sample is different) and the error $MAE$ along the iteration are displayed for each sound environment with the TI-NMF in the Figure \ref{fig:grafic_cost_mae}. After the 400 iterations, the cost functions for each sound environment, is very low meaning that the approximations of $\mathbf{V}$ by $\mathbf{WH}$ are very similar. However, they did not reach the convergence as the cost functions continue to decrease. Nevertheless, these behaviors have to be seen with the evolution of the $MAE$ error in Figure \ref{fig:grafic_mae}. For each sound environment, the traffic error reconstruction is constant after the 400 iterations which mean that the updates of $\mathbf{W}$ and $\mathbf{H}$ are dedicated to the interfering sound sources. Also, even if the cost function is higher for the \textit{very noisy street} than the \textit{park} sound environment, the $MAE$ error is lower due to the high presence of the \textit{traffic} component in it.

Finally, for TI-NMF, the influence of the number of elements $K$ in $\mathbf{W}$ and the size of the temporal frame $w_t$ on the $mMAE$ error are summarized in Figure \ref{fig:grafic_K_wt}. 
Naturally, with the increase of the number of basis in $\mathbf{W}$, the traffic error reconstruction decrease as it allows more basis to describe the traffic sound source. If this improvement is significant between 25 and 100 elements, its influence decrease between 100 and 200 elements suggesting that the increase of the size of $K$ will not improve a lot the quality of the estimation. In opposite, the temporal frame is not an influential  parameter for TI-NMF. As the matrices are updates, it is logical that the variations between the initial dictionary $\mathbf{W_0}$ due to this experimental factor disappear.
